
---
title:           Covid Testing Access
author:          Dennis Wollersheim  and Ali Lakhani
date:            25.07.2020
linkcolor:       cyan
citecolor:       grey
output:
  pdf_document:
    highlight:   zenburn
---

\tableofcontents


# initialisation
```{r init}

source('_drake.R')

loadd(df_covid_remoteness)
loadd(df_mesh_detail )
loadd(df_crow_distances )
loadd(df_mesh_in_reach )
loadd(df_population_in_reach )
loadd(df_driving_time )
loadd(df_distance_to_testing)
loadd( df_mesh_sa1 )
loadd( df_mesh_sa2 )

#df_mesh_correspondence %>% count(RA_CODE_2016 )

```


# driving time summary
The closer you are to a covid testing site, the faster it is to get there...

```{r }


df_driving_time %>%
  select(-starts_with('mc')) %>%
  inner_join( df_crow_distances %>%
             select(-starts_with('mc'), -starts_with('covid')),
                    by=c('MB_CODE16','id') ) %>%
  mutate(distance_category=cut(dist, breaks=0:12*5000, labels=make_labels(max_dist=60, divisor=5, descriptor='km'))) %>%
  group_by(id, distance_category) %>%
  summarise( duration = mean(duration, .groups='drop' )) %>%
  ggplot(aes( distance_category, duration) ) +
  geom_violin()




```


# what is the population access to testing


```{r}


df_distance_to_testing %>%
  inner_join(df_mesh_detail) %>%
  ggplot( aes( duration) ) + geom_histogram() +
  ggtitle( "Number of mesh blocks by time to drive to nearest testing site")


df_distance_to_testing %>%
  inner_join(df_mesh_detail) %>%
  mutate(duration_category=cut(duration, breaks=0:12*10, labels=make_labels(max_dist=120, divisor=10, descriptor='min'))) %>%
  group_by( duration_category) %>%
  summarise( persons = sum(Person)) %>%
  ggplot( aes( duration_category, persons) ) +
    geom_col() +
  ggtitle( "Population within N minutes of closest testing site ")


```

closest testing site to mesh block

How many mesh blocks / population are closest to a test site

for each mesh block, find the closest test site (as crow flies )
for each test site, how many mesh blocks / population / average road distance  to these closest mesh blocks

testing site x closest population, number of mesh blocks

remoteness of testing site (based on shape file)

```{r}
```



marry mesh block into sa2 -


which SA's have shortest and longest travel times to testing sites

average traveltime Meshblock per sa1


sa1 x avg travel time, sa2 x avg travel time


```{r csv }

```



marry mesh block into sa2 -


which SA's have shortest and longest travel times to testing sites

average traveltime Meshblock per sa1


sa1 x avg travel time, sa2 x avg travel time


```{r other_csv }

```
